\chapter{\HelloWorldSectionName}
\label{sec:helloworld}

\RU{Продолжим, используя знаменитый пример из книги}
\EN{Let's use the famous example from the book}
\ES{Continuemos usando el famoso ejemplo del libro}
``The C programming Language''\cite{Kernighan:1988:CPL:576122}:

\lstinputlisting{patterns/01_helloworld/hw.c}

\section{x86}

\input{patterns/01_helloworld/MSVC_x86}
\ifdefined\IncludeGCC
\input{patterns/01_helloworld/GCC_x86}
\fi

\section{x86-64}
\input{patterns/01_helloworld/MSVC_x64}
\ifdefined\IncludeGCC
\input{patterns/01_helloworld/GCC_x64}
\fi

\ifdefined\IncludeGCC
\input{patterns/01_helloworld/GCC_one_more}
\fi
\ifdefined\IncludeARM
\input{patterns/01_helloworld/ARM/main}
\fi
\ifdefined\IncludeMIPS
\input{patterns/01_helloworld/MIPS/main}
\fi

\section{\Conclusion{}}

\RU{Основная разница между кодом x86/ARM и x64/ARM64 в том, что указатель на строку теперь 64-битный.}
\EN{The main difference between x86/ARM and x64/ARM64 code is that pointer to the string is now 64-bits in length.}
\ES{La principal diferencia entre el código x86/ARM y x64/ARM64 es que el puntero a la cadena ahora es de 64 bits.}
\RU{Действительно, ведь для того современные \ac{CPU} и стали 64-битными, потому что подешевела память,
её теперь можно поставить в компьютер намного больше, и чтобы её адресовать, 32-х бит уже
недостаточно.}
\EN{Indeed, modern \ac{CPU}s are now 64-bit due to both the reduced cost of memory and the greater demand for it by modern applications. 
We can add much more memory to our computers than 32-bit pointers are able to address.}
\ES{En efecto, las \ac{CPU} modernas son de 64 bits porque la memoria se abarató y ahora se puede instalar mucha más; para direccionarla, 32 bits ya no bastan.}
\RU{Поэтому все указатели теперь 64-битные.}\EN{As such, all pointers are now 64-bit.}\ES{Por eso todos los punteros son ahora de 64 bits.}

% sections
\ifdefined\IncludeExercises
\input{patterns/01_helloworld/exercises}
\fi
